Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-05-26 draft_p2.tex
Update figure illustr_AMS #1

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{illustr_AMS/figure_AMS}
  \caption{\label{fig:illustr_AMS} Selection-mutation procedure of the \ac{ams} algorithm to compute the probability that a real-valued observable $A(\mathbf{x}(t))$ reaches values larger than $Q$ throughout a trajectory of duration $T_a$.\EL{QUID of the score function mentioned in the text: is the observable? \#1} The initial ensemble of blue trajectories (associated with the time evolution of the observable $A$) is first generated. These trajectories are independent and can be simulated in parallel. On the basis of the respective maxima $Q_1$, $Q_2$ and $Q_3$, the trajectory with the lowest maximum is discarded in the ensemble (dashed blue line). Among the two remaining trajectories, trajectory 3 is chosen randomly and copied until it reaches the value $Q_1$. It is then freely simulated from the branching point to the final time $T_a$. In case of deterministic dynamics, a small perturbation is introduced at the branching to separate the trajectories. This procedure is iterated $J$ times or until all trajectories exceed a fixed threshold $Q$.}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{illustr_AMS/illustr_AMS}
  \caption{\label{fig:illustr_AMS} Selection-mutation procedure of the \ac{ams} algorithm with $N=3$. Lines 1, 2 and 3 respresent the evolution of the score function for the current ensemble of trajectories. On the basis of their respective maximum $Q_1$, $Q_2$ and $Q_3$, the trajectory with the lowest maximum is discarded in the ensemble (dashed line). Among the two remaining trajectories, trajectory 3 is chosen randomly and copied until it reaches the value $Q_1$. It is then simulated from the branching point to the final time $T_a$. In case of deterministic dynamics, a small perturbation is introduced at the branching to separate the trajectories. Depending on the application, this resampling procedure can iterated $J$ times or until all trajectories exceed a fixed threshold $Q$. \TL{MAJ figure et ordonnee \#1}}
\end{figure}
